Concurrent Programming with CXL

### 2020-06-27 book/paper.tex
Starting to add screenshots

\begin{figure}
\begin{code}
\begin{verbatim}
#states = 79
==== Safety violation ====
CXL Assertion failed ('assert', 'Up.cxl', 9, 5): 1
__init__/() [0,34-49]       50 dict{.count:0, .done:dict{0:False, 1:False}}
incrementer/0 [1-4]          5 dict{.count:0, .done:dict{0:False, 1:False}}
incrementer/1 [1-10]        11 dict{.count:1, .done:dict{0:False, 1:True }}
incrementer/0 [5-10]        11 dict{.count:1, .done:dict{0:True,  1:True }}
main/() [13-17,20-24,26-31] 31 dict{.count:1, .done:dict{0:True,  1:True }}
\end{verbatim}
\end{code}
\caption{The output of running Figure~\ref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
#states = 79 diameter = 5
==== Safety violation ====
__init__/() [0,34-49]       50 dict{.count:0, .done:dict{0:False, 1:False}}
incrementer/0 [1-4]          5 dict{.count:0, .done:dict{0:False, 1:False}}
incrementer/1 [1-10]        11 dict{.count:1, .done:dict{0:False, 1:True }}
incrementer/0 [5-10]        11 dict{.count:1, .done:dict{0:True,  1:True }}
main/() [13-17,20-24,26-31] 31 dict{.count:1, .done:dict{0:True,  1:True }}
>>> CXL Assertion failed : 1
Open file://.../cxl.html for more information
\end{verbatim}
\end{code}
\caption{The text output of running CXL on Figure~\ref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/Up1.png}
\caption{The HTML output of running CXL on Figure~\ref{fig:inc}.}
\label{fig:inchtml1}
\end{figure}
